\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdfborder={0 0 0},
  breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-2}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother


\date{}

\begin{document}

\hypertarget{before-you-can-use-the-jobs-api-you-need-to-set-up-an-access-token.}{%
\section{Before you can use the jobs API, you need to set up an access
token.}\label{before-you-can-use-the-jobs-api-you-need-to-set-up-an-access-token.}}

\hypertarget{log-in-to-the-ibm-q-experience.-under-account-generate-a-personal}{%
\section{Log in to the IBM Q experience. Under ``Account'', generate a
personal}\label{log-in-to-the-ibm-q-experience.-under-account-generate-a-personal}}

\hypertarget{access-token.-replace-put_your_api_token_here-below-with-the-quoted}{%
\section{access token. Replace `PUT\_YOUR\_API\_TOKEN\_HERE' below with
the
quoted}\label{access-token.-replace-put_your_api_token_here-below-with-the-quoted}}

\hypertarget{token-string.-uncomment-the-apitoken-variable-and-you-will-be-ready-to-go.}{%
\section{token string. Uncomment the APItoken variable, and you will be
ready to
go.}\label{token-string.-uncomment-the-apitoken-variable-and-you-will-be-ready-to-go.}}

APItoken =
`fa990f5e816bd5f800fc269a9b3f4fbe85c11f8969ea229ecc7a247c97f100ae5324c5fbedec09aa89db39db83e013b61cac3ed5ad10bded16e3080026f7b388'

config = \{ `url': `https://quantumexperience.ng.bluemix.net/api',

\begin{verbatim}
# If you have access to IBM Q features, you also need to fill the "hub",
# "group", and "project" details. Replace "None" on the lines below
# with your details from Quantum Experience, quoting the strings, for
# example: 'hub': 'my_hub'
# You will also need to update the 'url' above, pointing it to your custom
# URL for IBM Q.
'hub': None,
'group': None,
'project': None
\end{verbatim}

\}

if `APItoken' not in locals(): raise Exception(`Please set up your
access token. See Qconfig.py.')

\end{document}
